\bf\mftitle

### 2011-02-24 doc/jInfer/projecttype/projecttype.tex
#3187361 projecttype doc

With each project created in jInfer is also created specific directory structure on filesystem that describes jInfer project. This structure is described in figure \ref{dir-structure}, where rectangles represent folders and rounded rectangles files. Folder in filesystem is considered as jInfer project folder, if contains \emph{jinferproject} subfolder. This folder contains two files, first is \emph{project.properties}, where all properties set for particular project are saved. Second file is \emph{input.files} which is xml file filled with paths to files inserted as input into particular project (structure of this file is described in section \ref{input.files}). \emph{Output} subfolder contains schema files which were generated by jInfer inference.

@@

\code{InputFiles} is utility class that stores/loads input file paths into/from input.files xml file. For this purpose, class uses \emph{JAXB} \cite{JAXB} architecture to unmarshall/marshall xml file into/from java content objects. Xml structure of the input.files is very simple, \emph{jinferinput} is root element under which are \emph{xml}, \emph{schemas} and \emph{queries} elements. Each of this elements could have none or more \emph{file} elements with string attribute \emph{loc} that contains absolute path to input file.\\

@@

@@

>>>>

With each project created in jInfer is also created specific directory structure on filesystem that describes jInfer project. This structure is described in figure \ref{dir-structure}. Folder in filesystem is considered as jInfer project folder, if contains \emph{jinferproject} subfolder. This folder contains two files, first is \emph{project.properties}, where all properties set for particular project are saved. Second file is \emph{input.files} which is XML file filled with paths to files inserted as input into particular project (structure of this file is described in section \ref{input.files}). \emph{Output} subfolder contains schema files which were generated by jInfer inference.

@@

\code{InputFiles} is utility class that stores/loads input file paths into/from input.files XML file. For this purpose, class uses \emph{JAXB} \cite{JAXB} architecture to unmarshall/marshall XML file into/from java content objects. XML structure of the input.files is very simple, \emph{jinferinput} is root element under which are \emph{documents}, \emph{schemas} and \emph{queries} elements. Each of this elements could have none or more \emph{file} elements with string attribute \emph{loc} that contains absolute path to input file.\\

@@

Each node in project tree hierarchy contains set of actions available from its context menu. Besides standard actions for root node or file node, jInfer project type introduce its own actions. These actions could be separated into three groups: actions for \emph{root} node, actions for \emph{input folder} nodes and one action for \emph{input/output file} nodes implemented by \code{ValidateAction} class. All classes implementing some jInfer project action extend standard java \code{javax.swing.AbstractAction} class besides \code{ValidateAction} class which is described in \ref{validate-action}.\\

\subsubsection{Root node actions}

This group contains two actions, first is action that allows adding input files into \emph{input folder} nodes (implemented by \code{FilesAddAction} class). Second one is slightly different, because unlike from the previous action, this one doesn't create new item in \emph{root} node context menu but implements functionality for item that already exists in context menu - Run action.\\

First of the two actions, after it was invoked, open file choose dialog which has set file filter according to available classes that implement \code{Processor} interface registered in jInfer with \code{ServiceProvider}. After selecting files in dialog, these files are inserted into particular \emph{input file} node according to mapping of file extension to folder type gained from \code{Processor} classes.\\

Run action, which is available in root node context menu, is also present in NBP toolbar as a \emph{Run} button and in jInfer Welcome window. This action is implemented in \code{RunAction} class and simply invokes \jmodule{Runner}s \code{run()} method, if no other inference is already running, otherwise information dialog pops up informing about already running inference. This check is done with \code{setActiveProject()} from \code{RunningProject} class.

\subsubsection{Input folder node actions}

To this group of actions belong two actions: action for adding input files into \emph{input folder} node (\code{FileAddAction} class) and action for deleting all input files in \emph{input folder} node (\code{DeleteAllAction} class). \code{FileAddAction} class implements action which opens file choose dialog and selected files are added into particular \emph{file input}node. \code{DeleteAllAction} class simply removes all input files previuosly added into particular \emph{file input} node.

\subsubsection{ValidateAction class}\label{validate-action}

\code{ValidateAction} class implements action, which allows documents and schema files to be validated against each other. Because of this, action is presented in context menu of document and schema files (in actual implementation is available for XML, dtd and XML schema files). Unlike the other action classes, this extends NBP \code{NodeAction} class, which allows to enable/disable action in context menu according to node selection. Action is enabled only if exactly one schema file is selected and one or more XML files. If the selected XML files are valid against selected schema, information dialog is popped up, otherwise error dialog is popped up and in \emph{validate} output window is printed error message describing cause of non-validity XML files against schema.

@@

Each jInfer project has associated properties window through which can user change project-wide properties. This window is accesible through \emph{properties} action in project \emph{root} node context menu. Properties window consists of category tree on a left side and properties pane on a right side. For each category in tree is associated one properties pane. Classes responsible for creation of this properties window are \code{JInferCustomizerProvider} and \code{JInferComponentProvider}.
